Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-01-06 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
resolved some todos
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4573 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
fix typo in formula (5)
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4574 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\setlength{\arraycolsep}{0.0em}
\begin{multline}
\label{eq:cost2}
Cost_{cut} = \sum_{n=1}^{N_{nets}} C' \times bbHeight(i) \times N_{crossed}(n)
\end{multline}

@@

Systems with more dice are slower; on average the critical path delay is xx\% higher for a four-die system than a two-die system. This speed difference is not significantly affected by the \textit{\% wires cut}.
\begin{figure}[!htbp]
\centering
\input{crit_path_4part}
\caption{Impact of number of dice on critical path delay.}
\label{fig:crit_path_4part}
\end{figure}

>>>>

\setlength{\arraycolsep}{0.0em}
\begin{multline}
\label{eq:cost2}
Cost_{cut} = \sum_{n=1}^{N_{nets}} C' \times bbHeight(n) \times N_{crossed}(n)
\end{multline}

@@

Systems with more dice are slower; on average the critical path delay is 40\% higher for a four-die system than a two-die system. This speed difference is not significantly affected by the \textit{\% wires cut}.
\begin{figure}[!htbp]
\centering
\input{crit_path_4part}
\caption{Impact of number of dice on critical path delay.}
\label{fig:crit_path_4part}
\end{figure}
